---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# highlightr

<!-- badges: start -->
<!-- badges: end -->

This work was funded (or partially funded) by the Center for Statistics and Applications in Forensic Evidence (CSAFE) 
through Cooperative Agreements 70NANB15H176 and 70NANB20H019 between NIST and Iowa State University, which includes activities carried 
out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, 
University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.

## Installation

You can install the development version of highlightr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rachelesrogers/highlightr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(highlightr)
## basic example code
```

