---
title: "highlightr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{highlightr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package is designed to map a group of individuals' notes to the corresponding parent text, based on the frequency with which phrases occur in the individual notes.
The parent text is highlighted corresponding to this frequency, in order to create a 'heatmap' of popular phrases found in the note sheets.

This example is taken from the initial description of a crime used in a study of jury perception of algorithm use and demonstrative evidence.

The first step is to re-assign names in the notepad text to correspond with the expected format used in `tokenize_derivative()` and use the function to tokenize the comments.

```{r}

# load the library
library(highlightr)

# tokenize comments
toks_comment <- tokenize_derivative(notepad_example, source_row=which(notepad_example$ID=="source"), text_column = "Text")
```

The next step is to tokenize the transcript in a similar manner.

```{r}

# tokenize source document
toks_transcript <- tokenize_source(notepad_example, source_row=which(notepad_example$ID=="source"), text_column = "Text")
```

After that, a fuzzy collocation is used to match the tokenized notes to the phrases in the tokenized transcript.
This function first determines the number of times a collocation of length 5 occurs in participant notes.
Fuzzy (or indirect) matches are then added to the frequency count of the transcript collocation that is the closest match.
These fuzzy matches are weighted based on the edit distance between the transcript collocation and the indirect phrase:
$$
\frac{n*d}{m}
$$

Here, $n$ is the frequency of the fuzzy collocation, $d$ is the Jaccard similarity between the fuzzy collocation and the transcript collocation (ranging from 0 to 1, where 1 indicates identical strings), and $m$ is the number of closest matches for the fuzzy collocation.


Next, the `collocation_frequency()` function attaches the collocation counts to the full text of the transcript.
<!-- This provides additional information about the original formatting of the transcript that is needed when constructing the final object. -->
The collocation frequencies are averaged per word.

```{r}

# connect collocation frequencies to source document

merged_frequency <- collocation_frequency(notepad_example[which(notepad_example$ID=="source"),][["Text"]], toks_transcript, toks_comment, fuzzy=TRUE)
```

The combined document is then fed through ggplot to assign gradient colors based on frequency, and the minimum and maximum values are recorded.

```{r}

# create `ggplot` object of the transcript

freq_plot <- collocation_plot(merged_frequency)
```

```{r}

# add html tags to source document

page_highlight <- highlighted_text(freq_plot)

```

After colors have been assigned, HTML output is created for highlighted text is created based on frequency, as well as a gradient bar indicating the high and low values.
The left side of each word gradient indicates the frequency of the previous word's averaged collocation frequency, while the right side indicates the current word's averaged collocation frequency.
This HTML output can be rendered into highlighted text by specifying `` `r '\x60r page_highlight\x60'` `` in an R Markdown document outside of a code chunk and knitting to HTML:

`r page_highlight`  

<br>

Alternatively, the `xml2` package can be used to save the output as an html file, as shown in the following code:

```{r, eval=FALSE}

# load `xml2` library

library(xml2)

# save html output to desired location

xml2::write_html(xml2::read_html(page_highlight), "filename.html")

```

In this case, the highlighting pattern resembles that when the fuzzy matches are included, but the maximum value reached is smaller.
Note also that the colors used in highlighting can be changed in the "colors" argument of the `collocation_plot` function.

```{r}

# connect collocation frequencies to source document

merged_frequency_nonfuzzy <- collocation_frequency(notepad_example[which(notepad_example$ID=="source"),][["Text"]], toks_transcript, toks_comment)

# create a `ggplot` object of the transcript, and change colors of the gradient

freq_plot_nonfuzzy <- collocation_plot(merged_frequency_nonfuzzy, colors=c("#15bf7e", "#fcc7ed"))

# add html tags to source document

page_highlight_nonfuzzy <- highlighted_text(freq_plot_nonfuzzy)
```

`r page_highlight_nonfuzzy`

<br>

Additionally, the length of the collocation can be changed.
The default collocation length (shown above) is 5 words.
Below, this collocation length has been changed to 2 words.

In these shorter collocations, we can see that the collocation containing the name "Richard Cole" is popular, with a frequency of 89.

```{r}

# connect collocation frequencies to source document

merged_frequency_2col <- collocation_frequency(notepad_example[which(notepad_example$ID=="source"),][["Text"]], toks_transcript, toks_comment, collocate_length = 2)

# create a `ggplot` object of the transcript

freq_plot_2col <- collocation_plot(merged_frequency_2col)

# add html tags to source document

page_highlight_2col <- highlighted_text(freq_plot_2col)
```

`r page_highlight_2col`
